A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
better adtree experimental section

We experimented the algorithm using various combinations of those two parameters.

@@

  \end{tabular}
  \caption{Results for ADTree.}
  \label{tbl:results_adtree}
  \end{center}
\end{table}

From Table \ref{tbl:results_adtree} we can see that the number of boosting iterations affects
both the execution time (directly proportional) and the error rate.
The best error rate is for the parameters \textbf{-E -2 -B 20} giving $\approx$19.80\% for the test set.

@@

>>>>

We experimented the algorithm using various combinations of those two parameters.
Tables \ref{tbl:results_adtree_discr} and \ref{tbl:results_adtree_raw} show
results for both discretized data and raw data, respectively.
An example tree built using non-discretized data and with the parameters \textbf{-E -2 -B 10}
is displayed in Listing \ref{decision_tree_adtree}.

@@

  \end{tabular}
  \caption{Results for ADTree for discretized data.}
  \label{tbl:results_adtree_discr}
  \end{center}
\end{table}

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} & \textbf{Nodes} & \textbf{Leaves} \\ \hline
    -E -3 -B 2 & 19.90 & 19.69 & 0m4.166s & 7 & 5 \\ \hline
    -E -3 -B 5 & 18.43 & 18.58 & 0m7.070s & 16 & 11 \\ \hline
    -E -3 -B 10 & 14.98 & 19.68 & 0m14.188s & 31 & 21 \\ \hline
    -E -3 -B 15 & 14.78 & 20.18 & 0m24.777s & 46 & 31 \\ \hline
    -E -3 -B 20 & 14.48 & 19.88 & 0m36.194s & 61 & 41 \\ \hline
    -E -3 -B 25 & 14.08 & 18.87 & 0m51.563s & 76 & 51 \\ \hline
    -E -3 -B 30 & 13.80 & 18.49 & 1m11.919s & 91 & 61 \\ \hline
    -E -3 -B 35 & 13.74 & 18.65 & 1m32.886s & 106 & 71 \\ \hline
    -E -3 -B 40 & 13.65 & 18.98 & 1m54.094s & 121 & 81 \\ \hline

    -E -2 -B 2 & 19.90 & 19.69 & 0m3.995s & 7 & 5 \\ \hline
    -E -2 -B 5 & 18.43 & 18.58 & 0m5.502s & 16 & 11 \\ \hline
    -E -2 -B 10 & 15.14 & 20.07 & 0m8.662s & 31 & 21 \\ \hline
    -E -2 -B 15 & 14.67 & 20.26 & 0m11.982s & 46 & 31 \\ \hline
    -E -2 -B 20 & 14.67 & 19.95 & 0m15.543s & 61 & 41 \\ \hline
    -E -2 -B 25 & 14.43 & 19.88 & 0m19.500s & 76 & 51 \\ \hline
    -E -2 -B 30 & 14.34 & 19.85 & 0m22.929s & 91 & 61 \\ \hline
    -E -2 -B 35 & 14.26 & 20.00 & 0m27.735s & 106 & 71 \\ \hline
    -E -2 -B 40 & 14.05 & 19.71 & 0m32.832s & 121 & 81 \\ \hline

    -E -1 -B 2 & 19.90 & 19.69 & 0m4.093s & 7 & 5 \\ \hline
    -E -1 -B 5 & 18.43 & 18.58 & 0m5.414s & 16 & 11 \\ \hline
    -E -1 -B 10 & 15.14 & 20.07 & 0m8.459s & 31 & 21 \\ \hline
    -E -1 -B 15 & 14.67 & 20.26 & 0m11.937s & 46 & 31 \\ \hline
    -E -1 -B 20 & 14.67 & 19.95 & 0m15.430s & 61 & 41 \\ \hline
    -E -1 -B 25 & 14.43 & 19.88 & 0m19.413s & 76 & 51 \\ \hline
    -E -1 -B 30 & 14.34 & 19.85 & 0m22.973s & 91 & 61 \\ \hline
    -E -1 -B 35 & 14.26 & 20.00 & 0m27.246s & 106 & 71 \\ \hline
    -E -1 -B 40 & 14.05 & 19.72 & 0m32.555s & 121 & 81 \\ \hline

    -E 0 -B 2 & 19.90 & 19.69 & 0m4.039s & 7 & 5 \\ \hline
    -E 0 -B 5 & 18.43 & 18.58 & 0m4.901s & 16 & 11 \\ \hline
    -E 0 -B 10 & 15.15 & 20.10 & 0m6.701s & 31 & 21 \\ \hline
    -E 0 -B 15 & 14.80 & 20.65 & 0m8.409s & 46 & 31 \\ \hline
    -E 0 -B 20 & 14.50 & 20.27 & 0m9.858s & 61 & 41 \\ \hline
    -E 0 -B 25 & 14.37 & 20.41 & 0m11.057s & 73 & 49 \\ \hline
    -E 0 -B 30 & 14.21 & 20.28 & 0m12.712s & 88 & 59 \\ \hline
    -E 0 -B 35 & 13.99 & 19.45 & 0m14.145s & 103 & 69 \\ \hline
    -E 0 -B 40 & 14.04 & 20.21 & 0m15.273s & 118 & 79 \\ \hline

  \end{tabular}
  \caption{Results for ADTree for non-discretized data.}
  \label{tbl:results_adtree_raw}
  \end{center}
\end{table}

From tables \ref{tbl:results_adtree_discr} and \ref{tbl:results_adtree_raw}
we can see that the number of boosting iterations affects
both the execution time (directly proportional) and the error rate.
The best error rate for raw data is using the parameters \textbf{-E -1 -B 5} giving $\approx$18.58\% for the test set.

For nearly all parameters the algorithm gives best results when using numeric attributes instead
of categories. Non-discretized data also generates larger trees.

@@

\clearpage
\begin{lstlisting}[language=c,frame=single,breaklines=true,basicstyle=\footnotesize\ttfamily,caption={Decision tree built by ADTree with -E -2 -B 10},label=decision_tree_adtree]
: -0.574
|  (1)marital_status = married_civ_spouse: 0.467
|  (1)marital_status != married_civ_spouse: -0.756
|  (2)capital_gain < 7073.5: -0.11
|  |  (5)capital_loss < 1748: -0.047
|  |  (5)capital_loss >= 1748: 0.996
|  |  (7)education = masters: 0.714
|  |  (7)education != masters: -0.055
|  (2)capital_gain >= 7073.5: 2.636
|  (3)age < 27.5: -0.891
|  (3)age >= 27.5: 0.11
|  (4)hours_per_week < 41.5: -0.183
|  (4)hours_per_week >= 41.5: 0.291
|  (6)education = bachelors: 0.418
|  (6)education != bachelors: -0.101
|  (8)education = prof_school: 0.986
|  (8)education != prof_school: -0.023
|  (9)education = doctorate: 1.067
|  (9)education != doctorate: -0.021
|  (10)occupation = exec_managerial: 0.335
|  (10)occupation != exec_managerial: -0.062
\end{lstlisting}
